---
title: "Bri Scratch"
author: Bri Cirillo
output: html_notebook
---

# February 25 2020

## Installing Mosaic

```{r}
#install.packages("mosaic")
#library(mosaic)

library(readxl)
Propagule_Data <- read_excel("Propagule Data.xlsx", 
    sheet = "Sheet1")

Propagule_Data=Propagule_Data[-4,]

```

## Descriptive Stats

### Distance Traveled
```{r}
# Descriptives on Distance Traveled in meters
distance <- fav_stats(Propagule_Data$DistanceTraveled.m)
distance

# Histogram of distance traveled
hist(Propagule_Data$DistanceTraveled.m, col = "Light Green", main = "Distance Traveled", xlab= "Distance Traveled (m)", ylab="Count")

# Scatter plot of distance traveled
plot(Propagule_Data$DistanceTraveled.m, col = "Light Green", main = "Distance Traveled", ylab= "Distance Traveled (m)", xlab="Count", pch=16)
```

Looking at the descriptives, the average distance traveled was 181.86 meters, with a standard deviation of 98.08. The high standard deviation 

### Drop Density
```{r}
# Descriptives on Drop Density
fav_stats(Propagule_Data$DropDensity)

# Descriptives of drop density when seperating for high and low density
densityH <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Density == "H"])
densityL <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Density == "L"])

#Plot showing just the spread of the points in drop density
plot(Propagule_Data$DropDensity, pch=16, col = "Sea Green", main = "Drop Density", xlab= "Drop Density", ylab="Count")

# Plot showing the drop density vs Distance traveled to hekp determine better break for high and low
plot(Propagule_Data$DropDensity, Propagule_Data$DistanceTraveled.m, pch=16, col = "Dark Olive Green", main = "Drop Density", ylab= "Distance Traveled", xlab="Drop Density")

```

#### Density Cut off

```{r}
# Shows the number of high density and the number of low
tally(Propagule_Data$Density)

# Shows the number of propagules with density <9
count <- tally(Propagule_Data$DropDensity < 9)
count
```

```{r}
# Creates a new column in the data that allows us to play with the density cut off
High.Density <-(Propagule_Data$DropDensity > 12)
Propagule_Data$DensityNew[Propagule_Data$DropDensity >= 12] ="H"
Propagule_Data$DensityNew[Propagule_Data$DropDensity <12] ="L"

# Creates a histogram showing the distance traveled with high and low to see how the distributions compare
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$DensityNew, width=300, data = Propagule_Data, xlab= "Distance Traveled vs Density", xlim = c(0,400), breaks=15)
```


### Recovery Density
```{r}
# Descriptives on Recovery Density
fav_stats(Propagule_Data$RecoveryDensity)

# Creates a histogram of recovery density
hist(Propagule_Data$RecoveryDensity, col = "Dark Olive Green", main = "Recovery Density", xlab= "Recovery Density", ylab="Count")

# Creates a plot of recovery density
plot(Propagule_Data$DistanceTraveled.m, Propagule_Data$RecoveryDensity, pch=16, col = "Dark Olive Green", main = "Recovery Density", xlab= "Density Traveled", ylab="Recovery Density")
```


### Tide
```{r}
# Descriptive stats on tide broken up by high and low
tideH <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Tide == "H"])
tideL <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Tide == "L"])

# Side-by-side histogram of the tides high and low vs the distnace traveled
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Tide, width=300, data = Propagule_Data, main = "Distance Traveled vs Tide", xlab = "Distance Traveled", xlim = c(0,400), breaks=15, col = "cyan3")

```


### Zones

```{r}
# Descriptive stats on zone broken up by 1, 2, 3
zone1 <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "1"])
zone2 <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "2"])
zone3 <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "3"])

# histogram of zone 1 vs distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "1"], width=300, data = Propagule_Data,main= " Distanced Traveled vs Zone 1", xlab= "Distance Traveled", breaks = 15, col= "aquamarine2")

# histogram of zone 2 vs distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "2"], width=300, data = Propagule_Data,main= " Distanced Traveled vs Zone 2", xlab= "Distance Traveled", breaks = 15, col= "aquamarine2")

# histogram of zone 3 vs distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "3"], width=300, data = Propagule_Data, main= " Distanced Traveled vs Zone 3", xlab= "Distance Traveled", breaks = 15, col= "aquamarine2")

# histogram of zones 1, 2, and 3 vs distance traveled on one axis
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Zone, width=300, data = Propagule_Data, main = "Distance Traveled vs zone", xlab = "Distance Traveled", xlim = c(0,400), breaks=15, col= "aquamarine2")

# box plots for the zones vs distance traveled
boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Zone, col = "aquamarine2")
```

## Running Tests

### Kruskal Wallis Test for Distance Traveled vs Zone

```{r}
# Wanted more information on the kruskal wallis test in R
?kruskal.test

# Running the test on distance traveled and how that is affected by zone
kruskal.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone)

# Post hoc test(bonferroni) to see where the difference lies in the zones
pairwise.wilcox.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone, p.adjust.method = "bonferroni", conf.int = TRUE, conf.level=0.95, paired = FALSE)

```

This makes sense because the median 2 is much higher than 1 and 3, therefore there is a statistical significance between 1 and 2, and 2 and 3.


### Mann Whitney U Test for Density

```{r}
wilcox.test(Propagule_Data$DistanceTraveled.m~ Propagule_Data$Density, mu = 0, alt = "two.sided", conf.int = TRUE,conf.level=0.95, paired = FALSE )
```

### Mann Whitney U Test for Tide

```{r}
wilcox.test(Propagule_Data$DistanceTraveled.m~ Propagule_Data$Tide, mu = 0, alt = "two.sided", conf.int = TRUE,conf.level=0.95, paired = FALSE )
```

