---
title: "Mangrove Dispersion"
authors: Brooke Attardi, Brianna Cirillo, and Sam Cavalli
output: html_notebook
---
# Installing Packages

```{r}
#install.packages("mosaic")
#library(mosaic)

library(readxl)
Propagule_Data <- read_excel("Propagule Data.xlsx", 
    sheet = "Sheet1")

Propagule_Data=Propagule_Data[-4,]
```

# Descriptive Stats

## Drop Density
```{r}
# Descriptives on Drop Density
fav_stats(Propagule_Data$DropDensity)

# Descriptives of drop density when seperating for high and low density
densityH <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Density == "H"])
densityL <- fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Density == "L"])

# Plot showing just the spread of the points in drop density
plot(Propagule_Data$DropDensity, pch=16, col = "Sea Green", main = "Drop Density", xlab= "Drop Density", ylab="Count")

# Plot showing the drop density vs Distance traveled to hekp determine better break for high and low
plot(Propagule_Data$DropDensity, Propagule_Data$DistanceTraveled.m, pch=16, col = "Dark Olive Green", main = "Drop Density", ylab= "Distance Traveled", xlab="Drop Density")

```

### Density Cut off

```{r}
# Shows the number of high density and the number of low
tally(Propagule_Data$Density)

# Shows the number of propagules with density < 9
count <- tally(Propagule_Data$DropDensity < 9)
count

# Creates a new column in the data that allows us to play with the density cut off
DensityNew <-(Propagule_Data$DropDensity > 12)
Propagule_Data$DensityNew[Propagule_Data$DropDensity >= 12] ="H"
Propagule_Data$DensityNew[Propagule_Data$DropDensity <12] ="L"

# Creates a histogram showing the distance traveled with high and low to see how the distributions compare
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$DensityNew, width=300, data = Propagule_Data, xlab= "Distance Traveled vs Density", xlim = c(0,400), breaks=15)
```


## Recovery Density
```{r}
# Descriptives on Recovery Density
fav_stats(Propagule_Data$RecoveryDensity)

# Creates a histogram of recovery density
hist(Propagule_Data$RecoveryDensity, col = "Dark Olive Green", main = "Recovery Density", xlab= "Recovery Density", ylab="Count")

# Creates a plot of recovery density
plot(Propagule_Data$DistanceTraveled.m, Propagule_Data$RecoveryDensity, pch=16, col = "Dark Olive Green", main = "Recovery Density", xlab= "Density Traveled", ylab="Recovery Density")
```


## Distance Traveled
```{r}
# Descriptives on Distance Traveled in meters
distance <- fav_stats(Propagule_Data$DistanceTraveled.m)
distance

# Histogram of distance traveled
hist(Propagule_Data$DistanceTraveled.m, col = "Light Green", main = "Distance Traveled", xlab= "Distance Traveled (m)", ylab="Count")

# Scatter plot of distance traveled
plot(Propagule_Data$DistanceTraveled.m, col = "Light Green", main = "Distance Traveled", ylab= "Distance Traveled (m)", xlab="Count", pch=16)
```

Looking at the descriptives, the average distance traveled was 181.86 meters, with a standard deviation of 98.08. The high standard deviation 

### Distance Traveled by Zone
```{r}
# Descriptive stats on zone broken up by 1, 2, 3
fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "1"])
fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "2"])
fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "3"])

# histogram of zone 1 vs distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "1"], width=300, data = Propagule_Data,main= " Distanced Traveled vs Zone 1", xlab= "Distance Traveled", breaks = 15, col= "aquamarine2")

# histogram of zone 2 vs distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "2"], width=300, data = Propagule_Data,main= " Distanced Traveled vs Zone 2", xlab= "Distance Traveled", breaks = 15, col= "aquamarine2")

# histogram of zone 3 vs distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone == "3"], width=300, data = Propagule_Data, main= " Distanced Traveled vs Zone 3", xlab= "Distance Traveled", breaks = 15, col= "aquamarine2")

# histogram of zones 1, 2, and 3 vs distance traveled on one axis
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Zone, width=300, data = Propagule_Data, main = "Distance Traveled vs zone", xlab = "Distance Traveled", xlim = c(0,400), breaks=15, col= "aquamarine2")

# box plots for the zones vs distance traveled
boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Zone, col = "aquamarine2", main = "Distance Traveled By Zone", xlab = "Zone", ylab = "Distance Traveled")
```

### Distance Traveled by Tide (H/L)
```{r}
# Descriptive stats on tide broken up by high and low
fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Tide == "H"])
fav_stats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Tide == "L"])

# Side-by-side histogram of the tides high and low vs the distance traveled
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Tide, width=300, data = Propagule_Data, main = "Distance Traveled vs Tide", xlab = "Distance Traveled", xlim = c(0,400), breaks=15, col = "cyan3")

boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Tide, main="Distance Traveled by Tide", ylab="Distance Traveled", xlab="Tide", col= "cyan")
```

#### Distance Traveled by Drop Density (H/L)
```{r}
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Density, width=300, data = Propagule_Data, xlab= "Distance Traveled vs Drop Density", xlim = c(0,400), breaks=15)
boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Density, main="Distance Traveled by Drop Density", ylab="Distance Traveled", xlab="Density", col = "cyan")
```


# Qualitative Data Descriptives

## Propagules found in each zone, and each tide

```{r}
# This counts all propagules found in each zone 
tally(Propagule_Data$Zone)
favstats(~`DistanceTraveled.m`, `Zone`,  data = Propagule_Data)
# This counts ll propagules found in each tide, H or L
tally(Propagule_Data$Tide)
```

# Running Tests

## Kruskal Wallis Test: Zones
```{r}
# This is a non-parametric ANOVA. We run non-parametrics because the data is not normal. This will compare all data by the median (ex. Median distance travled in Zone 1, compared to Zone 2)

# Wanted more information on the kruskal wallis test in R
?kruskal.test

# Running the test on distance traveled and how that is affected by zone
kruskal.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone)
<<<<<<< HEAD
pairwise.wilcox.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone, p.adjust.method = "bonferroni", paired = FALSE)
```

### Mann-Whitney U Test: Tide and Drop Density

#### Density
```{r}
# This is a non-parametric T-test, because there are only two levels. This will compare the data by the median (ex. H/L drop density vs H/L tide)
wilcox.test(Propagule_Data$DistanceTraveled.m~ Propagule_Data$Density, mu = 0, alt = "two.sided", conf.int = T,conf.level=0.95, paired = FALSE )
```
#### Tide
```{r}
wilcox.test(Propagule_Data$DistanceTraveled.m~ Propagule_Data$Tide, mu = 0, alt = "two.sided", conf.int = T,conf.level=0.95, paired = FALSE )
```

# Post hoc test(bonferroni) to see where the difference lies in the zones
```{r}
pairwise.wilcox.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone, p.adjust.method = "bonferroni", conf.int = TRUE, conf.level=0.95, paired = FALSE)
```

## Mann Whitney U Test for Density

```{r}
wilcox.test(Propagule_Data$DistanceTraveled.m~ Propagule_Data$Density, mu = 0, alt = "two.sided", conf.int = TRUE,conf.level=0.95, paired = FALSE )
```

## Mann Whitney U Test for Tide

```{r}
wilcox.test(Propagule_Data$DistanceTraveled.m~ Propagule_Data$Tide, mu = 0, alt = "two.sided", conf.int = TRUE,conf.level=0.95, paired = FALSE )
```

# Package: "Moments"

```{r}
#install.packages("moments")
library(moments)
```

# Skewness and Kurtosis for Distance Traveled

```{r}
skewness(Propagule_Data$DistanceTraveled.m)
```

```{r}
kurtosis(Propagule_Data$DistanceTraveled.m)
```

# Nested

## Zone 1
### High Density: High Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="H"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="H"], xlab = "Zone 1", ylab = "Distance Traveled", col = "lavender", main = "Zone 1 High Density High Tide")
```

### High Density: Low Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="L"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="L"], xlab = "Zone 1", ylab = "Distance Traveled", col = "plum4", main = "Zone 1 High Density Low Tide")
```

### Low Density: High Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="H"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="H"], xlab = "Zone 1", ylab = "Distance Traveled", col = "darkorchid1", main = "Zone 1 Low Density High Tide")
```

### Low Density: Low Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="L"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "1" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="L"], xlab = "Zone 1", ylab = "Distance Traveled", col = "plum", main = "Zone 1 Low Density Low Tide")
```

## Zone 2
### High Density: High Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="H"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="H"], xlab = "Zone 2", ylab = "Distance Traveled", col = "pink", main = "Zone 2 High Density High Tide")
```

### High Density: Low Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="L"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="L"], xlab = "Zone 2", ylab = "Distance Traveled", col = "pink1", main = "Zone 2 High Density Low Tide")
```

### Low Density: High Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="H"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="H"], xlab = "Zone 2", ylab = "Distance Traveled", col = "thistle1", main = "Zone 2 Low Density High Tide")
```

### Low Density: Low Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="L"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "2" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="L"], xlab = "Zone 2", ylab = "Distance Traveled", col = "thistle2", main = "Zone 2 Low Density Low Tide")
```

## Zone 3
### High Density: High Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="H"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="H"], xlab = "Zone 3", ylab = "Distance Traveled", col = "deepskyblue1", main = "Zone 3 High Density High Tide")
```

### High Density: Low Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="L"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="H" & Propagule_Data$Tide=="L"], xlab = "Zone 3", ylab = "Distance Traveled", col = "deepskyblue3", main = "Zone 3 High Density Low Tide")
```

### Low Density: High Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="H"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="H"], xlab = "Zone 3", ylab = "Distance Traveled", col = "deepskyblue4", main = "Zone 3 Low Density High Tide")
```

### Low Density: Low Tide
```{r}
favstats(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="L"])

boxplot(Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone== "3" & Propagule_Data$Density=="L" & Propagule_Data$Tide=="L"], xlab = "Zone 3", ylab = "Distance Traveled", col = "dodgerblue2", main = "Zone 3 Low Density Low Tide")
```
# Install Bootstrapping Package

```{r}
# install.packages("devtools")
library(devtools)
# install_github("ddarmon/confcurve")
library(confcurve)
```
```{r}
Propagule_Data$DistanceTraveled.m
Propagule_Data$Zone <- as.factor(Propagule_Data$Zone)
Propagule_Data$Zone

Propagule_Data$Density
```

## Bootstrapping For Zone

```{r}
OneWayZone <- confcurve.oneway(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone,20000,0.95)
```
## Bootstrapping For Tide

```{r}
OneWayZone <- confcurve.oneway(Propagule_Data$DistanceTraveled.m, Propagule_Data$Tide,20000,0.95)
```
## Bootstrapping For Density

```{r}
OneWayZone <- confcurve.oneway(Propagule_Data$DistanceTraveled.m, Propagule_Data$Density,20000,0.95)
```






