---
title: "Daneshgar Mangroves"
author: "Samantha Cavalli"
output: html_notebook
---

# 25 February 2020

## Descriptives

```{r}
#install.packages("mosaic")
library("mosaic")
library(readxl)
Daneshgar_Mangrove_Data_Cleaned<-read_excel("/cloud/project/Daneshgar Mangrove Data Cleaned.xlsx", sheet = "Drop_Points_UTM")
Daneshgar_Mangrove_Data_Cleaned <- Daneshgar_Mangrove_Data_Cleaned[-4,]
```

```{r}
colnames(Daneshgar_Mangrove_Data_Cleaned)
```

```{r}

favstats(~`Distance traveled.m`, data = Daneshgar_Mangrove_Data_Cleaned)
favstats(~`Distance traveled.m`, `Zone`, data = Daneshgar_Mangrove_Data_Cleaned)

```


```{r}
hist(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, col = "blue", main = "Distance Traveled", xlab = "Distance Traveled (meters)")

histogram(~Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` | Daneshgar_Mangrove_Data_Cleaned$Zone, xlab = "Distance Traveled (meters)")
```
```{r}
#install.packages('ggplot2')
```
```{r}
hist(Daneshgar_Mangrove_Data_Cleaned$`Recovery Density`)
```
```{r}
plot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, xlab = "Distance Traveled" , ylab = "Drop Density", col = "green", pch = 16)

plot(Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, xlab = "Drop Density" , ylab = "Distance Traveled", col= "blue", pch = 16)
```

```{r}
tally(Daneshgar_Mangrove_Data_Cleaned$Density)
```
```{r}
hist(Daneshgar_Mangrove_Data_Cleaned$`Drop Density`)
```


```{r}
table(Daneshgar_Mangrove_Data_Cleaned$`Drop Density`)
```

```{r}
plot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$`Recovery Density`, pch = 19)
```

# 3 March 2020
## More Descriptives 

```{r}
plot(Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, pch = 19, xlab = "Drop Density", ylab = "Distance Traveled")
```
### Plots for density 

```{r}
plot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$`Drop Density`)
```

```{r}
hist(Daneshgar_Mangrove_Data_Cleaned$`Drop Density`)
hist(Daneshgar_Mangrove_Data_Cleaned$`Recovery Density`)
```
```{r}
hist(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, col = "blue", xlab ="Distance Traveled")
```



```{r}
favstats(~`Distance traveled.m`, `Density`, data = Daneshgar_Mangrove_Data_Cleaned)
```
```{r}
histogram(~Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` | Daneshgar_Mangrove_Data_Cleaned$Density, xlab = "Distance Traveled (meters)")
```

```{r}
favstats(~`Distance traveled.m`, `Tide`, data = Daneshgar_Mangrove_Data_Cleaned)
histogram(~Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` | Daneshgar_Mangrove_Data_Cleaned$Tide, xlab = "Distance Traveled (meters)")
```

## Package: "Moments"

```{r}
#install.packages("moments")
library(moments)
```

## Skewness and Kurtosis for Distance Traveled

```{r}
kurtosis(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`)
```
```{r}
skewness(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`)
```

## Boxplots

```{r}
boxplot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` ~ Daneshgar_Mangrove_Data_Cleaned$Zone, xlab = "Zone", ylab = "Distance Traveled", col = "yellow")


boxplot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` ~ Daneshgar_Mangrove_Data_Cleaned$Density, col="yellow", xlab = "Density", ylab = "Distance Traveled")

boxplot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` ~ Daneshgar_Mangrove_Data_Cleaned$Tide, col="yellow", xlab = "Tide", ylab = "Distance Traveled")
```


# Kruskal Wallis

```{r}
kruskal.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$Zone)

pairwise.wilcox.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$Zone, p.adjust.method = "bonferroni", paired = FALSE, conf.int=TRUE)
```

# Mann-Whitney

```{r}
Daneshgar_Mangrove_Data_Cleaned$DensityReCode=Daneshgar_Mangrove_Data_Cleaned$`Drop Density`
Daneshgar_Mangrove_Data_Cleaned$DensityReCode[Daneshgar_Mangrove_Data_Cleaned$`Drop Density`<= 10]=1
Daneshgar_Mangrove_Data_Cleaned$DensityReCode[Daneshgar_Mangrove_Data_Cleaned$`Drop Density` > 10]=2
```

Recoded: drop density less than or equal to 10 as a 1 and greater than 1 as 2 

## Density
```{r}
wilcox.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`~ Daneshgar_Mangrove_Data_Cleaned$Density, mu = 0, alt = "two.sided", conf.int = T,conf.level=0.95, paired = FALSE )
```
## Tide
```{r}
wilcox.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`~ Daneshgar_Mangrove_Data_Cleaned$Tide, mu = 0, alt = "two.sided", conf.int = T,conf.level=0.95, paired = FALSE )
```
## Recoded Density (10 instead of 5)

```{r}
wilcox.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`~ Daneshgar_Mangrove_Data_Cleaned$DensityReCode, mu = 0, alt = "two.sided", conf.int = T,conf.level=0.95, paired = FALSE )
```
Ran this again using the new recoded density, with 10 as the threshold instead of 5. Pvalue is lower but still not significant. 

```{r}
tally(HuntersMangroveData2$Recovered)
```

# Chi Square

```{r}
table(HuntersMangroveData2$Density, HuntersMangroveData2$Recovered)
chisq.test(HuntersMangroveData2$Density, HuntersMangroveData2$Recovered)
denschi$expected
```
```{r}
table(HuntersMangroveData2$Tide, HuntersMangroveData2$Recovered)
chisq.test(HuntersMangroveData2$Tide, HuntersMangroveData2$Recovered)
tidechi$expected
```

# Regression

```{r}
scatter.smooth(x=Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, y=Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, main="Distance~Density", xlab = "Drop Density", ylab = "Distance Traveled", pch = 16, col="blue")

smooth.spline(x=Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, y=Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`)
```

```{r}
glm1 <- glm(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m` ~ Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, data = Daneshgar_Mangrove_Data_Cleaned)
summary.out = summary(glm1)
summary(glm1)
plot(glm1)
plot(density(glm1$residuals,bw="SJ"))
```
```{r}
Daneshgar_Mangrove_Data_Cleaned$lndensity=Daneshgar_Mangrove_Data_Cleaned$`Drop Density`
Daneshgar_Mangrove_Data_Cleaned$lndensity= log(Daneshgar_Mangrove_Data_Cleaned$`Drop Density`)

Daneshgar_Mangrove_Data_Cleaned$lndistancetrav=Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`
Daneshgar_Mangrove_Data_Cleaned$lndistancetrav= log(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`)

```

```{r}
scatter.smooth(x=Daneshgar_Mangrove_Data_Cleaned$lndensity, y=Daneshgar_Mangrove_Data_Cleaned$lndistancetrav, main="Distance~Density", xlab = "Drop Density", ylab = " ln Distance Traveled", pch = 16, col="blue")
```

```{r}
#install.packages('devtools')
library(devtools)

#install_github('ddarmon/confcurve')

```

```{r}
library(confcurve)
```

```{r}
bcd.out <- bootcurve.lm(`Distance traveled.m`~ `Drop Density`, data = Daneshgar_Mangrove_Data_Cleaned)
```

```{r}
plot.confcurve(bcd.out, param = 2)
plot.confcurve(lm(`Distance traveled.m`~`Drop Density`, data = Daneshgar_Mangrove_Data_Cleaned), param = 2, add=TRUE, col="red")
```
```{r}
confpvalue(bcd.out, theta = 0, param = 2)
confcurve(bcd.out, 0.95, param = 2)
```

P-value from bootstrapping

red curve = t distribution
black curve = bootstrap distribution

## Sign Test

```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone ==1], alternative="two.sided", conf.level = 0.95)
```
```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone ==2], alternative="two.sided", conf.level = 0.95)
```
```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone ==3], alternative="two.sided", conf.level = 0.95)
```




```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[ Daneshgar_Mangrove_Data_Cleaned$`Density`== "H"],alternative="two.sided", conf.level = 0.95)
```
```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[ Daneshgar_Mangrove_Data_Cleaned$`Density`== "L"],alternative="two.sided", conf.level = 0.95)
```

```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[ Daneshgar_Mangrove_Data_Cleaned$`Tide`== "L"],alternative="two.sided", conf.level = 0.95)
```

```{r}
SignTest(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[ Daneshgar_Mangrove_Data_Cleaned$`Tide`== "H"],alternative="two.sided", conf.level = 0.95)
```

## KS Test

```{r}
ks.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$Zone, p.adjust.methods = "bonferroni")
```

```{r}
ks.test(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, Daneshgar_Mangrove_Data_Cleaned$DensityCode, p.adjust.methods = "bonferroni")
```
```{r}
Daneshgar_Mangrove_Data_Cleaned$DensityCode=Daneshgar_Mangrove_Data_Cleaned$Density
Daneshgar_Mangrove_Data_Cleaned$DensityCode[Daneshgar_Mangrove_Data_Cleaned$Density== "L"]=1
Daneshgar_Mangrove_Data_Cleaned$DensityCode[Daneshgar_Mangrove_Data_Cleaned$Density == "H"]=2
```

Density: High = 2
        Low = 2
        
## Colored Plot

```{r}
gf_point(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`~Daneshgar_Mangrove_Data_Cleaned$`Drop Density`, data = Daneshgar_Mangrove_Data_Cleaned, col = ~ Zone, main= "Distance~Density", xlab = "Density", ylab = "Distance Traveled")
```

# Bootstrap with Recovery Density

```{r}
bcr.out <- bootcurve.lm(`Distance traveled.m`~ `Recovery Density`, data = Daneshgar_Mangrove_Data_Cleaned)


```

```{r}
plot.confcurve(bcr.out, param = 2)
plot.confcurve(lm(`Distance traveled.m`~`Recovery Density`, data = Daneshgar_Mangrove_Data_Cleaned), param = 2, add=TRUE, col="red")
```
```{r}
confpvalue(bcr.out, theta = 0, param = 2)
confcurve(bcr.out, 0.95, param = 2)
```

```{r}
scatter.smooth(x=Daneshgar_Mangrove_Data_Cleaned$`Recovery Density`, y=Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`, main="Distance~Recovery Density", xlab = "Recovery Density", ylab = "Distance Traveled", pch = 16, col="blue")
```

```{r}
gf_point(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`~Daneshgar_Mangrove_Data_Cleaned$`Recovery Density`, data = Daneshgar_Mangrove_Data_Cleaned, col = ~ Zone, main= "Distance~Density", xlab = "Recovery Density", ylab = "Distance Traveled")
```

# Zone 1 Descriptives 

## High vs low density

```{r}
boxplot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone== "1"] ~ Daneshgar_Mangrove_Data_Cleaned$Density[Daneshgar_Mangrove_Data_Cleaned$Zone== "1"], xlab = "Zone 1", ylab = "Distance Traveled", col = "yellow")
```

## High vs low tide 

```{r}
boxplot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone== "1"] ~ Daneshgar_Mangrove_Data_Cleaned$Tide[Daneshgar_Mangrove_Data_Cleaned$Zone== "1"], xlab = "Zone 1", ylab = "Distance Traveled", col = "yellow")
```

## High density and low tide 

```{r}
boxplot(Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone== "1" & Daneshgar_Mangrove_Data_Cleaned$Density=="H" & Daneshgar_Mangrove_Data_Cleaned$Tide=="L"], xlab = "Zone 1", ylab = "Distance Traveled", col = "yellow")
```
```{r}
favstats((Daneshgar_Mangrove_Data_Cleaned$`Distance traveled.m`[Daneshgar_Mangrove_Data_Cleaned$Zone== "1" & Daneshgar_Mangrove_Data_Cleaned$Density=="H" & Daneshgar_Mangrove_Data_Cleaned$Tide=="L"]))
```

