---
title: "Brooke Scratch"
output: html_notebook
---

# Februrary 25 2020

```{r}
# Installing Packages
#install.packages("mosaic")
library(mosaic)
library(readxl)
Propagule_Data <- read_excel("/cloud/project/Propagule Data.xlsx", 
    sheet = "Sheet1")
Propagule_Data <- Propagule_Data[-4, ]
```

## Descriptive Stats

### Drop Density
```{r}
favstats(Propagule_Data$DropDensity)
hist(Propagule_Data$DropDensity, main="Propagule Drop Density", xlab="Drop Density")
```

### Recovery Density
```{r}
favstats(Propagule_Data$RecoveryDensity)
hist(Propagule_Data$RecoveryDensity, main="Propagule Recovery Density", xlab="Recovery Density")
```

### Distance Traveled
```{r}
fav_stats(Propagule_Data$DistanceTraveled.m)
hist(Propagule_Data$DistanceTraveled.m, main="Propagule Distance Traveled", xlab="Distance Traveled")
```

# Februrary 27 2020

## More Descriptives
### Distance Traveled by Zone, Tide, and Drop Density (H/L)
```{r}
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Zone, width=300, data = Propagule_Data, xlab= "Distance Traveled vs zone", breaks=15)
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Tide, width=300, data = Propagule_Data, xlab= "Distance Traveled vs Tide", xlim = c(0,400), breaks=15)
histogram(~Propagule_Data$DistanceTraveled.m | Propagule_Data$Density, width=300, data = Propagule_Data, xlab= "Distance Traveled vs Drop Density", xlim = c(0,400), breaks=15)
```
# March 3rd 2020
```{r}
# Fixing the histograms of distance traveled by zone so we can see a better representation of how zone effects distance traveled
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone =="1"], width=300, main="Zone 1", xlab= "Distance Traveled", breaks=15)
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone =="2"], width=300, main="Zone 2", xlab= "Distance Traveled", breaks=15)
histogram(~Propagule_Data$DistanceTraveled.m[Propagule_Data$Zone =="3"], width=300, main="Zone 3", xlab= "Distance Traveled", breaks=15)
```


## Qualitative Data Descriptives
### Propagules found in each zone, and each tide
```{r}
# This counts all propagules found in each zone 
tally(Propagule_Data$Zone)
favstats(~`DistanceTraveled.m`, `Zone`,  data = Propagule_Data)
# This counts ll propagules found in each tide, H or L
tally(Propagule_Data$Tide)
```


## Running Tests
### Kruskal Wallis Test: Zones
```{r}
# This is a non-parametric ANOVA. We run non-parametrics because the data is not normal. This will compare all data by the median (ex. Median distance travled in Zone 1, compared to Zone 2)
kruskal.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone)
pairwise.wilcox.test(Propagule_Data$DistanceTraveled.m, Propagule_Data$Zone, p.adjust.method = "bonferroni", paired = FALSE)
```

### Mann-Whitney U Test: Tide and Drop Density
```{r}
# This is a non-parametric T-test, because there are only two levels. This will compare the data by the median (ex. H/L drop density vs H/L tide)

wilcox.test(Propagule_Data$DistanceTraveled.m, )

```
# March 5th 2020
### Adding some more Descriptives: Boxplots
#### By Zone
```{r}
# Adding boxplots to descriptive stats since we are looking at the medians in KS test
boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Zone)
```
#### By Drop Density (H/L)
```{r}
boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Density)
```

#### By Tide (H/L)
```{r}
boxplot(Propagule_Data$DistanceTraveled.m~Propagule_Data$Tide)
```

